Generation of Variation and Mean Fitness Increase: \\ Necessity is the Mother of Genetic Invention

### 2018-01-30 ms.tex
quorom sensing and rival assessment

In our final example, we consider a large population and an integer phenotype $k$ where $1 \le k \le n$.
Individuals are characterized by their initial and mature phenotypes~\citep[pg.~94]{Boyd1985}.
Fitness is determined by the mature phenotype: the fitness of an individual with mature phenotype $k$ is $w_k$.

@@

>>>>

In our final example, we consider a large population and an integer phenotype $k$ where $1 \le k \le n$.
Individuals are characterized by their initial and mature phenotypes~\citep[pg.~94]{Boyd1988}.
Fitness is determined by the mature phenotype: the fitness of an individual with mature phenotype $k$ is $w_k$.

@@

How can individuals estimate their fitness relative to the population mean fitness? 
In microbes, empirical evidence suggests that the mutation rate is negatively-correlated with population density~\citep{Krasovec2017} and is probably regulated by quorum sensing mechanisms~\citep{Krasovec2014,Dellus-Gur2017}.
Animals can assess the well-being of other individuals, for example via rival and mutual assessment~\citep{Parker1974,Arnott2017,Reichert2017}, and possibly integrate these assessments over a population sample.
Our results suggest that these assessment might affect the tendency of individuals to generate variation, e.g. explore new environments and behaviors.
